The Evolution of Phenotypically Invariant Genetic Networks

### 2017-08-04 kalman_walk_paper.tex
another note

First, since $(P + \epsilon Q)^{-1} = P^{-1} + \epsilon P^{-1} Q P^{-1}$,
modifying $P \to P + \epsilon Q$ changes
$$\begin{aligned}
    A 
        &\to A + \epsilon P^{-1} \hat A Q - \epsilon P^{-1} Q P^{-1} \hat A P \\
        &= A + \epsilon \left(A P^{-1} Q - P^{-1} Q A\right) , \\
    B
        &\to B - \epsilon P^{-1} Q B \\
    C
        &\to C + \epsilon C P^{-1} Q .
\end{aligned}$$

Then, $\hat A \to A + \epsilon X$  does
$$\begin{aligned}
    A \to A + \epsilon P^{-1} X P 
\end{aligned}$$
and $\hat B \to B + \epsilon Y$ does
$$\begin{aligned}
    B \to B + \epsilon P^{-1} Y
\end{aligned}$$
and $\hat C \to C + \epsilon Z$ does
$$\begin{aligned}
    C \to C + \epsilon Z P .
\end{aligned}$$

This gives us an upper bound on the number of degrees of freedom.
However, some of these may be redundant.
For instance, changing $P$ in the direction of 
a $Q$ that satisfies both $A P^{-1} Q = P^{-1} Q A$ and $C P^{-1} Q = 0$
is equivalent to changing $B$ by $Y = QB$.

>>>>

First, since $(P + \epsilon Q)^{-1} = P^{-1} + \epsilon P^{-1} Q P^{-1}$,
modifying $P \to P + \epsilon Q$ changes
$$\begin{aligned}
    A 
        &\to A + \epsilon P^{-1} \hat A Q - \epsilon P^{-1} Q P^{-1} \hat A P \\
        &= A + \epsilon \left(A P^{-1} Q - P^{-1} Q A\right) , \\
    B
        &\to B - \epsilon P^{-1} Q B \\
    C
        &\to C + \epsilon C P^{-1} Q .
\end{aligned}$$
Since $P$ is invertible and $Q$ can be anything (if $\epsilon$ is small enough),
this allows changes in the direction of an arbitrary $W$:
$$\begin{aligned}
    A 
        &= A + \epsilon \left(A W - W A\right) , \\
    B
        &\to B - \epsilon W B \\
    C
        &\to C + \epsilon C W .
\end{aligned}$$

Then, $\hat A \to A + \epsilon X$  does
$$\begin{aligned}
    A \to A + \epsilon P^{-1} X P 
\end{aligned}$$
and $\hat B \to B + \epsilon Y$ does
$$\begin{aligned}
    B \to B + \epsilon P^{-1} Y
\end{aligned}$$
and $\hat C \to C + \epsilon Z$ does
$$\begin{aligned}
    C \to C + \epsilon Z P .
\end{aligned}$$
These degrees of freedom depend on $P$, but both through the change of basis $P$
and the form of allowable $X$, $Y$, and $Z$.

This gives us an upper bound on the number of degrees of freedom.
\plri{maybe? depending on if choice of $P$ affects anything.}
However, some of these may be redundant.
For instance, changing $P$ in the direction of 
a $Q$ that satisfies both $A P^{-1} Q = P^{-1} Q A$ and $C P^{-1} Q = 0$
is equivalent to changing $B$ by $Y = QB$.
